---
title: "Sandbox"
author: "Eren Akgunduz"
date: "26 April 2023"
output:
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# The data, wrangled and cleaned/tidied

```{r, message=FALSE}
library(tidyverse)
df <- read.csv("data/all.csv", stringsAsFactors = FALSE)
```

## Make sure it's clean

```{r}
# Check for missing values
na_rows <- df[!complete.cases(df), ]
na_rows
```

## Validate before we really begin

```{r}
c(nrow(df), ncol(df))
dim(df) # same thing
summary(df)
str(df)
```
\

# Module 1: Information (description)

Descriptive stats, here mainly seeking to answer the question: how do the distributions look?

## Attacks for all characters

```{r, message=FALSE}
library(tidyverse)
df <- read.csv("data/all.csv", stringsAsFactors = FALSE)
```

### Character numerical features summary (averages)

```{r}
# transpose so we print vertically
t(colMeans(df[9:18]))
```

### Attack categorical features summary tables

```{r}
# define the function to create each summary table
summary_tb <- function(feature) {
  df %>%
    group_by({{ feature }}) %>%
    summarise(
      count = n(),
      average_damage = mean(Damage),
      average_stun = mean(Stun)
    ) %>%
    arrange(desc(average_damage))
}
```

```{r}
# call for each feature with its name as argument
summary_tb(plnCmd)
summary_tb(moveType)
summary_tb(airmove)
summary_tb(followUp)
summary_tb(projectile)
```

### Kernel density estimates (KDEs)

```{r}
desc <- function(variable) {
  sprintf(
    "Median: %.2f  |  Mean: %.2f  |  Standard deviation: %.2f",
    median(variable),
    mean(variable),
    sd(variable)
  )
}

desc(df$onBlock)
# user will be able to adjust bandwidth with slider
ggplot(df, aes(onBlock)) +
  geom_density(adjust = 1, linewidth = 1, lineend = "round")

desc(df$Damage)
ggplot(df, aes(Damage)) +
  geom_density(adjust = 1, linewidth = 1, lineend = "round")

desc(df$Stun)
ggplot(df, aes(Stun)) +
  geom_density(adjust = 1, linewidth = 1, lineend = "round")
```

## Attacks for each character

```{r, message=FALSE}
library(tidyverse)
```

### Putting it all together

```{r}
character_info <- function(datafile, char_name, img_path, kde_color) {
  df <- read.csv(datafile, stringsAsFactors = FALSE)

  # h1(char_name)
  # Counterclockwise on grid starting here, top left: display image
  # img(src = img_path)

  # Bottom left: KDEs
  desc <- function(variable) {
    sprintf(
      "Median: %.2f  |  Mean: %.2f  |  Standard deviation: %.2f",
      median(variable),
      mean(variable),
      sd(variable)
    )
  }

  print(desc(df$onBlock))
  # user will be able to adjust bandwidth with slider
  print(ggplot(df, aes(onBlock)) +
    geom_density(
      alpha = 0.2, adjust = 1, linewidth = 1.6,
      lineend = "round", fill = kde_color, color = kde_color
    ))

  print(desc(df$Damage))
  print(ggplot(df, aes(Damage)) +
    geom_density(
      alpha = 0.2, adjust = 1, linewidth = 1.6,
      lineend = "round", fill = kde_color, color = kde_color
    ))

  print(desc(df$Stun))
  print(ggplot(df, aes(Stun)) +
    geom_density(
      alpha = 0.2, adjust = 1, linewidth = 1.6,
      lineend = "round", fill = kde_color, color = kde_color
    ))

  # Bottom right: all attack attributes (9 columns)
  print(head(df[c(1:7, 18:19)])) # head only temporary to see if working

  # Top right: all character facts (10 columns but printed row-wise)
  print(t(df[1, 8:17])) # same idea as earlier
}
```

### Let's test em out

```{r}
# used Pika app to pick colors from images
character_info(
  "data/characters/abigail.csv",
  "Abigail",
  "img/abigail.png",
  "#af33b4"
)
character_info(
  "data/characters/akuma.csv",
  "Akuma",
  "img/akuma.png",
  "#a52e28"
)
character_info(
  "data/characters/alex.csv",
  "Alex",
  "img/alex.png",
  "#48683d"
)
character_info(
  "data/characters/balrog.csv",
  "Balrog",
  "img/balrog.png",
  "#235dbb"
)
character_info(
  "data/characters/birdie.csv",
  "Birdie",
  "img/birdie.png",
  "#d7a23e"
)
character_info(
  "data/characters/blanka.csv",
  "Blanka",
  "img/blanka.png",
  "#b36732"
)
character_info(
  "data/characters/cammy.csv",
  "Cammy",
  "img/cammy.png",
  "#67b600"
)
character_info(
  "data/characters/chun-li.csv",
  "Chun-Li",
  "img/chun-li.png",
  "#37659b"
)
character_info(
  "data/characters/cody.csv",
  "Cody",
  "img/cody.png",
  "#521f15"
)
character_info(
  "data/characters/dan.csv",
  "Dan",
  "img/dan.png",
  "#bf6072"
)
character_info(
  "data/characters/dhalsim.csv",
  "Dhalsim",
  "img/dhalsim.png",
  "#e0602b"
)
character_info(
  "data/characters/e_honda.csv",
  "E. Honda",
  "img/e_honda.png",
  "#5197a3"
)
character_info(
  "data/characters/ed.csv",
  "Ed",
  "img/ed.png",
  "#51bcd0"
)
character_info(
  "data/characters/f_a_n_g.csv",
  "F.A.N.G",
  "img/f_a_n_g.png",
  "#3040a0"
)
character_info(
  "data/characters/falke.csv",
  "Falke",
  "img/falke.png",
  "#191b44"
)
character_info(
  "data/characters/g.csv",
  "G",
  "img/g.png",
  "#3d453a"
)
character_info(
  "data/characters/gill.csv",
  "Gill",
  "img/gill.png",
  "#bf423b"
)
character_info(
  "data/characters/guile.csv",
  "Guile",
  "img/guile.png",
  "#597c00"
)
character_info(
  "data/characters/ibuki.csv",
  "Ibuki",
  "img/ibuki.png",
  "#4b1d40"
)
character_info(
  "data/characters/juri.csv",
  "Juri",
  "img/juri.png",
  "#983190"
)
character_info(
  "data/characters/kage.csv",
  "Kage",
  "img/kage.png",
  "#553fad"
)
character_info(
  "data/characters/karin.csv",
  "Karin",
  "img/karin.png",
  "#e93824"
)
character_info(
  "data/characters/ken.csv",
  "Ken",
  "img/ken.png",
  "#ff0000"
)
character_info(
  "data/characters/kolin.csv",
  "Kolin",
  "img/kolin.png",
  "#394057"
)
character_info(
  "data/characters/laura.csv",
  "Laura",
  "img/laura.png",
  "#80dc00"
)
character_info(
  "data/characters/lucia.csv",
  "Lucia",
  "img/lucia.png",
  "#3e77b1"
)
character_info(
  "data/characters/m_bison.csv",
  "M. Bison",
  "img/m_bison.png",
  "#480e07"
)
character_info(
  "data/characters/menat.csv",
  "Menat",
  "img/menat.png",
  "#3d224b"
)
character_info(
  "data/characters/nash.csv",
  "Nash",
  "img/nash.png",
  "#3a8455"
)
character_info(
  "data/characters/necalli.csv",
  "Necalli",
  "img/necalli.png",
  "#581e0d"
)
character_info(
  "data/characters/poison.csv",
  "Poison",
  "img/poison.png",
  "#d14461"
)
character_info(
  "data/characters/r_mika.csv",
  "R. Mika",
  "img/r_mika.png",
  "#68e6f7"
)
character_info(
  "data/characters/rashid.csv",
  "Rashid",
  "img/rashid.png",
  "#375963"
)
character_info(
  "data/characters/ryu.csv",
  "Ryu",
  "img/ryu.png",
  "#457272"
)
character_info(
  "data/characters/sagat.csv",
  "Sagat",
  "img/sagat.png",
  "#a16a46"
)
character_info(
  "data/characters/sakura.csv",
  "Sakura",
  "img/sakura.png",
  "#ff83fa"
)
character_info(
  "data/characters/seth.csv",
  "Seth",
  "img/seth.png",
  "#6d7293"
)
character_info(
  "data/characters/urien.csv",
  "Urien",
  "img/urien.png",
  "#714661"
)
character_info(
  "data/characters/vega.csv",
  "Vega",
  "img/vega.png",
  "#ed5971"
)
character_info(
  "data/characters/zangief.csv",
  "Zangief",
  "img/zangief.png",
  "#e52a0e"
)
character_info(
  "data/characters/zeku_old.csv",
  "Zeku (Old)",
  "img/zeku_old.png",
  "#545345"
)
character_info(
  "data/characters/zeku_young.csv",
  "Zeku (Young)",
  "img/zeku_young.png",
  "#351f0a"
)
```
\

# Module 2: Visualization

Are frames on block and damage+stun correlated? Let's find out.

```{r, message=FALSE}
library(tidyverse)
library(RColorBrewer)
df <- read.csv("data/all.csv", stringsAsFactors = FALSE)
```

## Tilemaps

```{r}
df_tile <- df %>%
  # convert to factor and reverse level order so it looks right on plot
  mutate(character_name = factor(Character,
    levels = rev(sort(unique(Character)))
  )) %>%
  # create intervals for plotting/colormap and similar to before, reverse order
  mutate(oB_bins = cut(onBlock,
    breaks = seq(from = -100, to = max(onBlock, na.rm = TRUE) + 2, by = 25)
  )) %>%
  mutate(oB_bins = factor(as.character(oB_bins), levels = rev(levels(oB_bins))))

# make sure the set of colors matches the number of bins
cmap_bins <- length(levels(df_tile$oB_bins))

tilemap <- function(responses, custompal) {
  print(ggplot(
    df_tile,
    aes(x = {{ responses }}, y = character_name, fill = oB_bins)
  ) +
    geom_tile(width = 10, color = "white", linewidth = 0.2) +
    coord_fixed(ratio = 10) +
    guides(fill = guide_legend(title = "Frames\non block")) +
    labs(y = "") +
    # removes extra space
    scale_y_discrete(expand = c(0, 0)) +
    # define new breaks on x-axis
    scale_x_continuous(
      expand = c(0, 0),
      limits = c(-10, 410),
      breaks = seq(from = 0, to = 400, by = 50)
    ) +
    scale_fill_manual(values = rev(brewer.pal(cmap_bins, custompal))) +
    # set a base size for all fonts
    theme_grey(base_size = 9) +
    # styling to make it my own
    theme(
      legend.title = element_text(color = "#292F36"),
      legend.text = element_text(size = 7, color = "#292F36"),
      legend.key.height = grid::unit(0.8, "cm"),
      legend.key.width = grid::unit(0.3, "cm"),
      axis.title.x = element_text(margin = margin(t = 8), color = "#292F36"),
      axis.text.x = element_text(color = "#292F36"),
      axis.text.y = element_text(color = "#292F36"),
      axis.ticks = element_line(linewidth = 0.4), # thickness of axis ticks
      plot.background = element_blank(), # rm background
      panel.border = element_blank() # rm outer border
    ))
}

tilemap(Damage, "YlGnBu") # will give user option to change to YlOrRd
tilemap(Stun, "YlGnBu")
```
